A data-intensive assessment of the species-abundance distribution.

### 2015-04-09 defense_pres.tex
Keeps reworking slides.

@@

\begin{frame}
\frametitle{Patterns \& process.}
\begin{huge}
\begin{center}
Process\\ 
\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPattern.png}\\
Pattern\\
\end{center}
\end{huge}
\end{frame}

@@

@@

\begin{frame}[t]
\frametitle{SAD Comparisons}
Identifying pattern generating mechanisms:
\begin{itemize}
\item Compare predictions of different models using multiple macroecological patterns simultaneously.\\
\end{itemize}
\begin{center}  
\includegraphics[scale=.4]{./sad-data/dissertation/MacroecologicalPatterns.png}
\end{center}
\end{frame}

\begin{frame}[t]
\frametitle{SAD Comparisons}
Identifying pattern generating mechanisms:
\begin{itemize}
\item Examine scale dependence of pattern.
\item More general approach to process.
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Neutral Analysis}
Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
\begin{center}
\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014AB.png}
\end{center}
\note{
\begin{small}
\begin{itemize}
\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
\end{itemize}
\end{small}}
May be a robust method for identifying communities that exhibit non-neutrality.\\
\end{frame}

\begin{frame}[t]
\frametitle{Neutral theory}
~\\
Many formulations, but:
~\\
\begin{itemize}
\item Species \& individuals ecologically \& demographically equivalent.\\
\end{itemize}
\includegraphics[scale=.35]{./sad-data/dissertation/Rosindelletal2011.png}\\
\begin{tiny}
Rosindell et al. 2011.
\end{tiny}
\note{
\begin{itemize}
\item Species \& individuals ecologically \& demographically equivalent.\\
\item Stochastic variation in birth, death, immigration, \& speciation results in species abundance differences.
\end{itemize}}
\end{frame}

>>>>

\begin{frame}
\frametitle{Pattern \& process.}
\note{
Few common species.
Many rare species.
One of the most fundamental and ubiquitous patterns in ecology.}
Species abundance distribution (SAD)
\begin{itemize}
\item Reveals pattern-generating mechanisms of community structure.
\end{itemize}
\begin{center}
\includegraphics[scale=.4]{./sad-data/dissertation/realistic_even_RAD.png}\\
\end{center}
\end{frame}

@@

\begin{frame}
\frametitle{Patterns \& process.}
\begin{Large}
\begin{center}
Process\\ 
\includegraphics[scale=.35]{./sad-data/dissertation/ProcessesPattern.png}\\
Pattern\\
\end{center}
\end{Large}
\end{frame}

@@

\section{Outline}
\begin{frame}

\end{frame}

@@

\begin{frame}[t]
\frametitle{Identifying process:}
\vspace{-7pt}
\begin{center}
\includegraphics[scale=.3]{./sad-data/dissertation/SpatialTaxonomic.png}
\end{center}
\begin{itemize}
\item Examine scale dependence of pattern.
\item More general approach to process?
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Neutral Analysis}
Connolly et al. 2014 simulated neutral communities.\\
\begin{center}
\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014A.png}
\end{center}
\note{
\begin{small}
\begin{itemize}
\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
\end{itemize}
\end{small}}
Identified a signal of neutrality.\\
\end{frame}

\begin{frame}
\frametitle{Neutral Analysis}
Connolly et al. 2014 identified non-neutral species abundance distributions in marine communities.\\
\begin{center}
\includegraphics[scale=.25]{./sad-data/dissertation/Connolly2014B.png}
\end{center}
\note{
\begin{small}
\begin{itemize}
\item Compared model fits of a non-neutral distribution (Poisson lognormal) to a neutral distribution (negative binomial distribution).\\
\end{itemize}
\end{small}}
May be a robust method for identifying communities that exhibit non-neutrality.\\
\end{frame}

\begin{frame}[t]
\frametitle{Neutral processes}
~\\
Many formulations of neutral theory, but:
~\\
\begin{itemize}
\item Species \& individuals ecologically \& demographically equivalent.\\
\end{itemize}
\includegraphics[scale=.35]{./sad-data/dissertation/Rosindelletal2011.png}\\
\begin{tiny}
Rosindell et al. 2011.
\end{tiny}
\note{
\begin{itemize}
\item Species \& individuals ecologically \& demographically equivalent.\\
\item Stochastic variation in birth, death, immigration, \& speciation results in species abundance differences.
\end{itemize}}
\end{frame}

\begin{frame}[t]
\frametitle{Non-neutral processes}
~\\
Many specific mechanisms, but:
~\\
\begin{itemize}
\item Shape of the abundance distribution due to differences among species.\\
\end{itemize}
\begin{center}
\includegraphics[scale=.2]{./sad-data/dissertation/non-neutral-processes.png}
\end{center}
\end{frame}
